MSE and dynamic state variable model with sigma function

### 2018-09-18 doc/MSE_MAR_18.tex
version that NA e-mailed to JJP
and that NA, ADR, and JJP worked on collectively

\abstract{Most worldwide fish stocks are overexploited, and so exploited beyond the maximum sustainable yield (MSY). The EU common fisheries policy, designed for the long-term environmental, economic, and social sustainability of fishing and aquaculture activities, includes making use of the MSY reference points as targets for exploiting commercially important fish stocks. To incentivise individual business to improve selectivity and avoid unwanted catches, it also introduced a landing obligation. Achieving these complex objectives may not necessarily reduce harvest rates, but will change the underlying selectivity patterns of harvests. The impact of exploiting at MSY and no discarding allowance on the optimal effort allocation between fleets is analyzed. We contrast two management plans to achieve MSY from two stocks and compare their effectiveness based on a management strategy evaluation that uses a dynamic state variable model including errors in decision-making in its operating model. The results show that when accounting for quota on one specie and for quotas on both species, MSY landings in the short-term are 30\% to 50\% lower than when compared to an unmanaged situation simulations. Some years after the implementation, MSY landings are similar or 25\% to 50\% higher than the pre-manage situtation. Optimal effort at MSY generates effort reductions of 37\% to 62\% over the mid-term, thus there would be some vessels that could benefit up to 1.4 times larger profits than before the CFP implementation. The results show taht for both species, any of the two management plans would be beneficial to both the stock and part of the fleets over the mid-term compared with the projections over the short-term.}

@@

\keywords{management strategy evaluation; dynamics state variable model; errors in decision-making; landing obligation; maximum sustainable yield}

@@

\begin{equation} \label{eq:solve}
P_{p}(C_i, Q_i, F_i, s) = \frac
                % Nominator
                {e^{ -\Delta_{p}(C_i, Q_i, F_i, s)/\sigma}}
                % Denominator
                {\sum_p e^{ -\Delta_{p}(C_i, Q_i, F_i, s)/\sigma}},
\end{equation}
where $\sigma$ was a tuning parameter that measured how important it was to be near the optimal choice. A large $\sigma$ resulted in uniform probabilities of choices, with vessels being distributed uniformly across the different fishing areas. In contrast, a small $\sigma$ forces vessels to concentrate in the optimal location (but note that $\sigma$ should be $> 0$). For computations, we used $\sigma = 3000$ (Table \ref{t:fishery}). %(noting that $\Delta$ ranged from 0 to $\sim 2 x 10^{3}$, but was generally of the order of $1 x 10^2$ in magnitude).

@@

Number of vessels                                           &                       & 8000           \\ 
Fuel costs (Euro fishing month\textsuperscript{-1})         &                       & 2000        \\ 
Gear maintenance (Euro fishing season\textsuperscript{-1})  &                       & 0               \\ 
Crew share                                                  &                       & 0\%        \\ 
Landing costs (Euro t\textsuperscript{-1})                  &                       & 0               \\
Optimal choice error                                        & $\sigma $             & 3000            \\

@@

% HARVEST RATES
Modelling results indicated that the age composition of the harvest was different during the post-manage than it was during the pre-manage period (Fig. \ref{f:selectivity}). In the pre-manage period harvesting above the $H_{max}$ (with values around 0.03, Fig. \ref{f:catches}) caused instability in both populations. Overharvesting was caused by more significant harvesting in juvenile specimens than in adults, with a downward sloping harvest rate curves over fish age (rather than selectively targeting older fish with higher price; Fig.4), with average harvest rates of 0.06 (Fig. \ref{f:selectivity} and \ref{f:yields}, black lines). These harvests and levels of biomass remained stable over time due to the constant recruitment introduced into the population dynamics. On the other hand, after the MP implementation, there was a immediate decrease in harvest rates with values equal to or below $H_{max}$. After a few years, in the mid-term, 2 to 6-year old fish were harvested at the same rate during the post-manage period, while yearling fish (age class 1) was harvested at lower rates (Fig. \ref{f:selectivity} and \ref{f:yields}, grey lines).

@@

Using a managent strategy evaluation framework, the potential consequences of two species quota scenarios were examined, allowing the evaluation of costs and benefits, both economic and in terms of risks to both stock and livelihoods, that resulted from the response of individual effort allocation to meet the objectives of the landing obligation regarding the objectives of the CFP, specially the MSY. The MSE framework included temporal and spatial key processes in the dynamics of two fish populations, the fisheries and the management body, and can be thought of as a minimum realistic model \cite{Punt1995, Kell2007}. The analysis extended earlier approaches which used short-term state-dependent decision-making models (e.g. \cite{Alzorriz2018, Batsleer2016, Poos2010} by including the consequent biomass of fish stocks and the management procedure to make its decision on how to respond to the state of the resource. If the landing obligation changes selectivity patterns as predicted in \cite{Alzorriz2018, Batsleer2016}, the use of the present MSE allows the evaluation on the reference points for sustainable exploitation in longer terms by explicitly modelling the feedback between fleet and stock dynamics. Nevertheless, the framework used made several assumptions: that there was perfect knowledge of the stochastic nature of catch rates, full compliance of fishers with the discarding policy, lack of transferability of individual quotas, and lack of interference competition among fishers \cite{Alzorriz2018}. Regarding fish populations, also important assumptions were established: constant mortality and almost neligible, constant recruitment along the years, equal conversion length to weight for the two species, constant migration that lead to a clear segregation of the youngers, age-dependant catchability assumed independent of age and equal for the two species and prices were age dependant but fixed over time. Also, we used monthly time steps in the model to keep computation time low, while the time scale at which fishing trips occur may be much smaller. Finally, we did not include the existence of any landing obligation discard flexibilities (CFP Article 15, \cite{CFP2013}) or year transfer swaps. We may thus have underestimated the flexibility of the fishery to respond to quota limitations imposed under the landing obligation. Despite these assumptions, the minimum realistic model developed in this study allowed us to simulate the dynamics of a mixed fishery fleet and examine whether potential harvest strategies can achieve the management objectives.

When the fishery was unmanaged, with unconstrained quota for both species (pre-manage period), the observed harvesting rates showed average values larger than the estimated average values that can be harvested in a sustainable manner ($H_{max}$), thus resulted in a situation where the stocks were overfished, reaching total catches of more than 4 tons per species (Fig. \ref{f:catches}), which in terms of activity would be fishing around 3100 days per area and season (Fig. \ref{f:catchesbyarea} and \ref{f:meaneffort} a and c). Given the spatial and price distribution of the species' parameters (Fig. \ref{f:distribution} and  \ref{f:prices}), fishing in both the northern and southern fishing grounds would be equally profitable. Our results suggested that 80\% of the fleet  indistinctly choosed harvesting in both areas, with net profits of 130 thousand Euros/ year (Fig. \ref{f:effort} b and d). Fuel costs related to fishing choices were 40\% of the incurred gross revenues (Fig. \ref{f:effort} b an d).

Moving from an unmanaged period to a situation where one or both species were regulated by quotas and forced to comply simulataneously with management objectives (i.e. exploiting at MSY and no discarding allowance) on the optimal effort allocation between fleets was analysed. For example, the underlying assumption of the two quota scenarios that fleets would switch targeted stocks to their relative abundance and management constraints was tested. Under both scenarios, our model results showed that simultaneously implementation of MSY and LO objectives led to a very restrictive fishing activity. Effort is constrained by some quota stock, as predicted in general terms by \cite{Ulrich2017}. Short-term reductions in effort would be needed while mid-term interactions between fleets and stocks that occur in mixed fisheries such as t

%Consequently, no comparisons could be made to verify the hypothesis stating that an effort regulation is more biologically robust as there are no incentives for discards and black landings. This hypothesis would be interesting to investigate in the model as, according to Faroese scientists, it seems to be one of the main advantages of this management system %(Jákupsstovu & Reinert, personal communication).

Achieving these complex objectives may not necessarily reduce harvest rates, but will change the underlying selectivity patterns of harvests. We contrast two management plans to achieve MSY from two stocks and compare their effectiveness based on a management strategy evaluation that uses a dynamic state variable model including errors in decision-making in its operating model. The results show that when accounting for quota on one specie and for quotas on both species, MSY landings in the short-term are 30\% to 50\% lower than when compared to an unmanaged situation simulations. Some years after the implementation, MSY landings are similar or 25\% to 50\% higher than the pre-manage situtation. Optimal effort at MSY generates effort reductions of 37\% to 62\% over the mid-term, thus there would be some vessels that could benefit up to 1.7 times larger profits than before the CFP implementation. The results show taht for both species, any of the two management plans would be beneficial to both the stock and part of the fleets over the mid-term compared with the projections over the short-term.

\begin{itemize}
\item{Simultaneously implementation of MSY and LO objectives may lead to a very restrictive fishing activity, at least, in the short-term. Effort is constrained by some stock, as predicted, in general terms, by Ulrich et al. (2011).}
\item{Drastic reduction of effort would increase profits if MSY and LO were contemplated. However, no flexibilities or year transfer swaps were considered. Be carefull if applying flexibilities, because as Prellezo 2016 (the results obtained from applying any kind of exemption or flexibility are, simply, negative) said, any increased in mortality beyond the MSY would be negative.}
\item{once the status of the stock has been assessed relative to its MSY level, the calculation of a TAC comes automatically from the rules of the Management Procedure. Shifting areas toward complying TAC limitations produced changes in selectivity ant therefore, constant changes in MSY levels. (e.g. shifting selectivity toward smaller/younger fish will generally reduce MSY). if it is required that the TAC should correspond to the level where MSY can be obtained, it will be necessary to monitor continuously the stock abundance and to revise TACs on a regular basis.}
\item{The  MSY under two quota species may be below what was achieved in one quota species because overall selectivity has shifted to smaller fish and low harvest of older fish; the impact of this change in selectivity on estimates of MSY is clearly seen in the results from Fig. \ref{f:selectivity} and \ref{f:yields}. While  the  potential  MSY  has decreased over time the stock biomass required to produce this MSY has increased.}
\item{Catch quota management is a more important mechanism than the actual obligation to land. An accurate and monitoring of all catches is a primary step towards sustainable and responsible fisheries.}
\item{The compliance of the fleets, the changes in behaviour and the availability and reliability of catch statistics (Catchpole and Riveiro Santos, 2015) . Data risks should not be overlooked (Hentati-Sundberg et al., 2014). Fish stock assessment provides the foundation for scientific advice to decision-makers on sustainable catch levels. A critical feature of stock assessment methodology is its dependence on accurate commercial data, which makes it susceptible to biased reporting (Walters and Maguire, 1996; Cotter et al., 2004; Bousquet et al., 2010). The reasons for misreporting and underreporting include e.g. IUU fishing (Agnew et al., 2009), discard obligation (Kelleher, 2005; Wielgus et al., 2010) and catches from recreational fisheries (Zeller et al., 2011). Such misreporting can be driven by fishing fleet overcapacity, resulting from restrictive TACs and/or effort regulations (Patterson, 1998; Beare et al., 2005; Dobby et al., 2008) that create economic incentives for non-compliance (Sumaila et al., 2006; Gallic and Cox, 2006; Osterblom et al., 2011).}

\end{itemize}

%When discarding was allowed, fishers did not avoid areas where catching undersized specimens was likely because there was no incentive to do so. Under all three implementations (scenarios) of the landing obligation, however, our model showed that the Basque trawling fleet was likely to move to areas with lower catch rates of quota species to avoid exceeding quota limitations. We showed that in the short term the landing obligation would likely result in a loss in profitability for the fleet. This loss in profitability was driven by the ``choke'' effect for species such as mackerel (scenario II and III), which was triggered by reductions in effort as a result of rapid quota exhaustion and by greater costs associated with fishing further from home ports (scenario IV).

%Our results suggest that the Basque fleet is limited by hake, horse mackerel and mackerel quota. In scenarios II and III, the choke effect of mackerel is so strong that the effect of other species limits (hake under scenario II, horse mackerel under scenario III) is negligible. Consequently, under both these scenarios our model predicts that the fleet will avoid using OTB gear and will reduce fishing effort in sub-area 7 and 8 because of their high mackerel catch rates (Fig. \ref{fig:effort_modelval}). Thus, fishers will likely visit sub-area 6 and 8 (using PTB gear). Revenues under these two scenarios are predicted to result in a loss of profitability (60\% less than the status quo; Table ~\ref{t:net_rev}). These findings indicate that trading quotas (at rates undertaken in the past) does not alleviate the choking effect of the landing obligation. Therefore, new ways of swapping quotas would be needed under the landing obligation to alleviate the choke effect of any of the quota limiting species. Fleets with high discards rates of certain species will be likely to have larger incentives to increase their quotas for those species than fleets with low discard rates.

%In scenario IV, the addition of inter-species quota-swapping flexibility to the landing obligation (e.g. 9\% of the horse mackerel catch quota could go to increase mackerel quota) substantially decreased the mackerel choke effect and increased both fishing opportunities and net revenues, when compared to scenarios II and III. Under this scenario, revenue was 30\% lower than when discarding was allowed (scenario I).

%Our results suggest that reductions in fishing opportunities under a landing obligation that are caused by choke species could be alleviated by the use of inter-species quota flexibility, and that there will be strong incentives to use this flexibility. Management bodies should ensure that the use of different flexibilities will constrain catches to comply with the MSY objective in Article 2(2) of the CFP Basic Regulation. Use of inter-species quota flexibility could cause serious impacts to stock abundance when quota from a high volume/low value species is transferred to a low volume/high value stock. Achieving a balance between quota flexibility, over-exploitation risk, and administrative simplicity is critical for the profitability and sustainability of multi-species fisheries.

%The success of any new regulation also depends on achieving a balance between the costs and benefits of measures that promote voluntary compliance and those that punish non-compliance. With poor enforcement the economic benefits of non-compliance outweigh the risks of detection \cite{Catchpole2005, Batsleer2013}. In our model, detection rates were assumed to be 100\% and fines were set sufficiently high so that no discarding occurred, reflecting full compliance with regulations. However, if detection rates are low and the short–term benefits of non-compliance are high (as our results suggest) then non-compliance is likely to be a substantial problem in the absence of measures promoting voluntary compliance.

%The landing obligation was implemented to incentivise individual businesses to improve selectivity and avoid unwanted catches. The landing obligation shifts the emphasis from prescribing the fishing gears that are permissible, to a results-based system where the onus is on the fishers to use fishing gear that will avoid unwanted catches. Therefore, fishers should be incentivised to develop alternative gear or adapt their fishing behaviour to mitigate the full impact of the landing obligation \cite{Alzorriz2016}. Discard ban policies may not necessarily reduce harvest rates but will change the underlying selectivity patterns of harvests \cite{Borges2016}. Our results reflect the short-term effects of a discard ban on selectivity patterns and net revenues implemented under three scenarios. If the landing obligation changes selectivity patterns as we predict, then we would also expect longer term changes in both fish populations and the economy of the fishery. Such analyses are the domain of bio-economic management strategy evaluations where the feedback between fleet and stock dynamics are modelled explicitly \cite{Andersen2010, Prellezo2016a, Punt2016}. In such models, effects of the changing selectivity of the fishing fleets on the reference points for sustainable exploitation can be evaluated.

>>>>

%Most worldwide fish stocks are overexploited, and so exploited beyond the maximum sustainable yield (MSY). 
\abstract{The EU common fisheries policy (CFP), designed for the long-term environmental, economic, and social sustainability of fishing and aquaculture activities, includes making use of the  maximum sustainable yield (MSY) reference points as targets for exploiting commercially important fish stocks. To incentivise individual business to improve selectivity and avoid unwanted catches, it also introduced a landing obligation. Achieving these complex objectives may not necessarily reduce harvest rates, but will change the underlying selectivity patterns of harvests. The impact of exploiting at MSY and no discarding allowance on the optimal effort allocation between fleets is analyzed. We contrast two management plans to achieve MSY from two stocks and compare their effectiveness based on a management strategy evaluation that uses a dynamic state variable model including errors in decision-making in its operating model. The results show that when accounting for quota on one specie and for quotas on both species, MSY landings in the short-term are 30\% to 50\% lower than when compared to an unmanaged situation simulations. Some years after the implementation, MSY landings are similar or 25\% to 50\% higher than the pre-manage situtation. Optimal effort at MSY generates effort reductions of 37\% to 62\% over the mid-term, thus there would be some vessels that could benefit up to 1.4 times larger profits than before the CFP implementation. The results show taht for both species, any of the two management plans would be beneficial to both the stock and part of the fleets over the mid-term compared with the projections over the short-term.}

@@

\keywords{management strategy evaluation; dynamics state variable model; errors in decision-making; landing obligation; maximum sustainable yield, common fisheries policy}

@@

\begin{equation} \label{eq:solve}
P_{p}(C_i, Q_i, F_i, s) = \frac
                % Nominator
                {e^{ -\Delta_{p}(C_i, Q_i, F_i, s)/\sigma}}
                % Denominator
                {\sum_p e^{ -\Delta_{p}(C_i, Q_i, F_i, s)/\sigma}},
\end{equation}
where $\sigma$ was a tuning parameter that measured how important it was to be near the optimal choice. A large $\sigma$ resulted in uniform probabilities of choices, with vessels being distributed uniformly across the different fishing areas. In contrast, a small $\sigma$ forces vessels to concentrate in the optimal location (but note that $\sigma$ should be $> 0$). For computations, we used $\sigma = 65000$ (Table \ref{t:fishery}). %(noting that $\Delta$ ranged from 0 to $\sim 2 x 10^{3}$, but was generally of the order of $1 x 10^2$ in magnitude).

@@

Number of vessels                                           &                       & 8000           \\ 
Fuel costs (Euro fishing month\textsuperscript{-1})         &                       & 2000        \\ 
Gear maintenance (Euro fishing season\textsuperscript{-1})  &                       & 0               \\ 
Crew share                                                  &                       & 0\%        \\ 
Landing costs (Euro t\textsuperscript{-1})                  &                       & 0               \\
Optimal choice error                                        & $\sigma $             & 65000            \\

@@

% HARVEST RATES
Modelling results indicated that the age composition of the harvest was different during the post-manage than it was during the pre-manage period (Fig. \ref{f:selectivity}). In the pre-manage period harvesting above the $H_{max}$ (with values around 0.03, Fig. \ref{f:catches}) caused instability in both populations. Overharvesting was caused by more significant harvesting in juvenile specimens than in adults, with a downward sloping harvest rate curves over fish age (rather than selectively targeting older fish with higher price; Fig. \ref{f:selectivity}), with average harvest rates of 0.06 (Fig. \ref{f:selectivity} and \ref{f:yields}, black lines). These harvests and levels of biomass remained stable over time due to the constant recruitment introduced into the population dynamics. On the other hand, after the MP implementation, there was a immediate decrease in harvest rates with values equal to or below $H_{max}$. After a few years, in the mid-term, 2 to 6-year old fish were harvested at the same rate during the post-manage period, while yearling fish (age class 1) was harvested at lower rates (Fig. \ref{f:selectivity} and \ref{f:yields}, grey lines).

@@

Our results suggest that in mixed fisheries, constraining quota for a single-species brought risk of eroding the production potential of unconstrained species when species differ only in spatial distribution. Both species in this study were the same with respect to growth, recruitment, mortality, and price, but differed in the location of their nursery habitat. The changes in production potential were caused by changing exploitation patterns in the fishery due to quota constraints in one species and the resulting spatial reallocation of fishing effort towards the nursery habitat of the other. The resulting change in age selectivity of the fishery decreased the production of the unmanaged stock (Fig. \ref{f:selectivity}).

Meanwhile, when constraining both species, the production potential of both stocks was maintained, that is to say the yield curves were unchanged. However, the stochastic nature of the catches combined with the individual quota result in individual fishers stopping when one of their quotas is reached. At the population level this results in overal cacthes that are lower than the TACs set based on the MSY principle. Such lack of achieving MSY in mixed fisheries with multiple single-species quota has been described elsewhere (xxxx,xxxx,xx), but thereit was attributed to a difference in the life-history characteristics of the different species. Here it is only because of schochasticiyty in catches that is pervasive in all fisheries.DEPENDS ON QUOTA TRADING, AND IF THAT IS POSSIBLE/ HOW GOOD IS MARKET

WHEN MOVING TO MSY HARVEST RATES THERE ARE FEW YEARS WITH REDUCED CATCHES LIKE CLASSICAL MODELS.

The forecasted effects of fisheries management in mixed fisheries result from individual choices by fishers on management and spatial heterogeneity in the resources rather than in differences in biological characestics of the resources. This emphsizes the need for incorporating detailed fishing dynamics. Histrocially, focus of management strategy evaluation has been primarily on managing the population (biological) dynamics of single and multispecies fisheries \cite{Butterworth1997, DelaMare1996, Dichmont2006, Punt1992, Punt1999, Punt2002, Smith1999}. Few MSE studies have explicitly incorporated the direct effects of human dimension harvesting on the stocks, although is equally important \cite{Fulton2011, Hilborn1985}. Human behaviour and decision-making are intrinsic parts of conservation and natural resource management. MSE with explicit human (social) behaviour dimension is increasingly being used \cite{Andersen2010, Ono2017} as fisheries science takes other sources of uncertainty to a greater extent to identify management actions that ensure the sustainability of fisheries.

Our modeling MSE approach use a dynamic state variable model, including fishing location choices and heterogeneous populations, to evaluate the costs and benefits, both economic and in terms of risks to both stock and livelihoods, that resulted in response of adopting a major policy change such as the CFP \cite{CFP2013}. Starting from an overfished mixed fishery under open access conditions but with a landing obligation constraint, where discarding is not allowed, the response of individual effort allocation and the interannual dynamics for both fleet dynamics and quota allocation is counted when adopting MSY objectives while landing all catches. The analysis extended earlier approaches which used short-term state-dependent decision-making models (e.g. \cite{Alzorriz2018, Batsleer2016, Poos2010}) by including the consequent biomass of fish stocks and the management procedure to make its decision on how to respond to the state of the resource. The MSE framework, was thought of as a minimum realistic model \cite{Kell2007, Punt1995}, and included temporal and spatial key processes in the dynamics of two fish populations, the fisheries and a reevaluation of management targets. To keep the model simple, the two fish populations modelled here are exactly the same apart from their spatial distribution difference (Fig. \ref{f:distribution}). As a result, if the landing obligation changes selectivity patterns in the shor-term as predicted in \cite{Alzorriz2018, Batsleer2016}, the present MSE modeling approach allows the evaluation on the reference points for sustainable exploitation in longer terms by explicitly modelling how changes in exploitation rates impact fish populations and yields. ERROR IN DECISION MAKING, NO DISCARING ALLOWED BY FISHERS, AND PERFECT COMPLIANCE TO THIS

When the studied mixed fishery was unmanaged, with unconstrained quota for both species (pre-manage period) and no discarding allowance, the observed harvesting rates showed average values larger than the estimated average values that can be harvested in a sustainable manner ($H_{max}$). Overfishing occurs in both stocks when fishers exceed $H_{max}$, whereas rebuilding requires reducing exploitation below $H_{max}$ (Fig. \ref{f:yields}).  Therefore, during the pre-manage period, a high exploitation rate caused a decline in total biomass and fishers mainly harvest the individuals that would normally be added to the population, with younger fish being targeted for. Our results suggested that given the spatial and price species distribution parameters (Fig. \ref{f:distribution} and \ref{f:prices}), fishing in both the northern and southern fishing grounds were equally profitable; thus, the distribution of fishing effort was equally distributed (Fig. \ref{f:effort}).

Moving from an unmanaged period to a situation where one or both species were quota regulated by implementing MSY objectives while maintaining a LO management regime (i.e. main CFP objectives: exploiting at MSY and no discarding allowance) led to a very restrictive fishing activity (Fig. \ref{f:effort}). Fishing effort was constrained by one or two quota stocks, as predicted in general terms by \cite{Ulrich2017}, resulting in drastic reductions of effort over the short-term and mid-term. In addition to reconciling fishery and conservation objectives (such as the CFP), in agreement with \cite{Grafton2007}, setting exploitation rates below $H_{max}$ resulted in a reduction in fishing cost and an increase in net revenue over the mid-term (Fig. \ref{f:effort}). However, as \cite{Prellezo2016a} concluded, since effort was drastically reduced to achieve the objectives of the CFP; the increase in net revenue gains were only experienced by some vessels. Consequently, a significant part of the fleet had to cease its activity (Fig. \ref{f:effort}).

Nevertheless, the framework used made several assumptions: that there was perfect knowledge of the stochastic nature of catch rates, full compliance of fishers with the discarding policy, lack of transferability of individual quotas, and lack of interference competition among fishers \cite{Alzorriz2018}. IMPORTANT< UTILITY FUNCTION IS ANNUAL NET REV, NO SOCIAL DYNAMICS. Regarding fish populations, also important assumptions were established: negligible natural mortality, constant recruitment, constant growth, constant migration, and constant size-dependent prices. Individual choices on fishing behaviour were assumed to be made once a month. However, despite these assumptions, the minimum realistic model developed in this study allowed us to simulate the dynamics of a mixed fishery and examine the effects of single species quota management.

In the study, the fishes were not allowed to discard, complying to a landings obligation.We did not include the use of any discard flexibilities of the LO (CFP Article 15, \cite{CFP2013}) or annaul quota swaps. Allowing the latter could potentially remedy the underutilisation of quota in the two quota situation, given that this reuslts from the stochsticity in catches, which are uncorrelated.

 We may thus have underestimated the flexibility of the fishery to respond to quota limitations imposed under both the landing obligation and exploiting at MSY. However, applying any kind of exemption or flexibility beyond the MSY would be negative \cite{Prellezo2016}. Consequently, a critical feature of management bodies is to ensure that the use of different flexibilities will constrain catches to comply with the MSY objective in Article 2(2) of the CFP Basic Regulation. Achieving a balance between quota flexibility, over-exploitation risk, and administrative simplicity is critical for the profitability and sustainability of multi-species fisheries \cite{Alzorriz2018}. The success of any new regulation also depends on achieving a balance between the costs and benefits of measures that promote voluntary compliance and those that punish non-compliance. With poor enforcement the economic benefits of non-compliance outweigh the risks of detection \cite{Catchpole2015, Batsleer2013}. In this MSE framework, detection rates were assumed to be 100\% and fines were set sufficiently high so that no discarding occurred, reflecting full compliance with regulations. However, if detection rates are low and the short-term benefits of non-compliance are high (as our results suggest) then non-compliance is likely to be a substantial problem in the absence of measures promoting voluntary compliance. IF YOU WANT TO STUDY THIS, THEN DETAILED PARAMETRIZATION IS NEEDED THAT INCLUDES CASE DEPENDENT LH CHARATRISTICS AND MIGRATIONS
 %Optimal effort at MSY generates effort reductions of 37\% to 62\% over the mid-term, thus there would be some vessels that could benefit up to 1.7 times larger profits than before the CFP implementation. The results highlighted the importance of accounting for technical interactions and their temporal dynamics in both quota allocation and fleet dynamics to design a realistic multispecies fishery management strategy analysis

Finally, a dynamic state variable model was used as a tool to create a quick quota allocation and fleet dynamics model. Many detailed fleet dynamics models have been developed over the past decades \cite{Abbott2011, Ono2017, Simons2015} and they could have been used to include spatial factors as another dimension in the MSE. However, following \cite{Dowling2011}, incorporating uncertainty in errors in human dynamic decision-making help us to understant and predict changes in human behaviour in response of adopting a major policy change such as the CFP \cite{CFP2013}. The effect of introducing a realistic multispecies fishery within this MSE framework still remains the next step to be taken. Modelling and predicting realistic human behavior with its associated uncertainty in an ever-changing socioecological system will remain a major challenge to address in the future \cite{Ono2017}.

\section{Conclusions}

Achieving optimal yield from mixed fisheries is a pervasive problem in fisheries management (e.g., \cite{Farcas2016, Prellezo2016b, Salomon2014, Ulrich2017, Voss2014}). A multispecies fishery MSE framework based on two populations was developed in this study to examine different management scenarios. The results highlight pitfalls in managing mixed fisheries where erosion of production potential can take place, or unintentional underharvesting. We argue for the inclusion of spatial dynamics and fleet dynamics when designing a multispecies fishery management strategy evaluation. Such MSE should be done  when adopting a major policy change such as the CFP. Future studies aimed at building a realistic multispecies fishery MSE with significant discard constraints, and should consider expanding the current model to include the whole suite of species exploited and managed in a real mixed fishery. The results highlighted the importance of accounting for technical interactions and their temporal dynamics in both quota allocation and fleet dynamics to design a realistic multispecies fishery management strategy analysis.
